---
title: "UN Votes Tidy Tuesday 23-01-2021"
output: html_notebook
---

The data this week comes from [Harvard's Dataverse](https://dataverse.harvard.edu/dataset.xhtml?persistentId=hdl:1902.1/12379) courtesy of Mine Çetinkaya-Rundel, David Robinson, and Nicholas Goguen-Compagnoni. Data is also available as an [R Package]("https://cran.r-project.org/web/packages/unvotes/unvotes.pdf") `{unvotes}`


```{r}
# Load in packages
library(tidytuesdayR)
library(tidyverse)
library(patchwork)
library(here)
library(lubridate)
library(ggpomological)
library(tidytext)
library(sf)
library(countrycode)
library(rnaturalearth)
```


```{r}
# Load in data 

tuesdata <- tidytuesdayR::tt_load('2021-03-23')

unvotes <- tuesdata$unvotes
roll_calls <- tuesdata$roll_calls
issues <- tuesdata$issues
```



# Map of countries and their voting tendencies

```{r}
# join country votes with rcid
un_votes_full <- unvotes %>%
  left_join(roll_calls, by = "rcid")
```


```{r}
# join country votes to issues
prop_yes <- un_votes_full %>%
  left_join(issues, by = "rcid") %>%
  # clean up country names not recogniced by countrycode
  mutate(country = case_when(str_detect(country, "Yemen") ~ "Yemen",
                             str_detect(country, "German") ~ "Germany",
                             TRUE ~ country)) %>%
  filter(year(date) > 1990) %>%
  group_by(country, issue) %>%
  # calculate proportion of resolutions each country voted for
  summarise(total_votes = n(),
            prop_yes = mean(vote == "yes")) %>%
  mutate(country_code = countrycode(country, origin = "country.name", destination = "iso3c")) %>%
  filter(!is.na(issue)) %>%
  drop_na(country_code)
  
# generate world map
world <- ne_countries(scale = "small", returnclass = "sf")

# plot proportion of yes votes by country as a chloropleth
map <- world %>%
  # join unvotes data to spatial data
  left_join(prop_yes, by = c("brk_a3" = "country_code")) %>%#
  # remove resolutions not assigned to an issue
  filter(!is.na(issue)) %>%
  ggplot() +
  geom_sf(aes(fill = prop_yes), size = 0.1, colour = "#828585") +
  # change map projection
  coord_sf(crs = 54030) +
  # set colour scale
  scale_fill_gradient2(low = "#c03728", mid = "#f5c04a", high = "#919c4c", midpoint = 0.5, 
                       name = "Proportion of \"Yes\" votes", 
                       guide = "colourbar", 
                       breaks = c(0.01, 0.5, 1), labels = c("0", "0.5", "1")
                      ) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0, nbin = 5)) +
  scale_color_pomological(guide = F) +
  theme_pomological(base_family = "Reenie Beanie", base_size = 20) +
  theme(axis.text = element_blank(),
        strip.text = element_blank(),
        legend.position = "bottom",
        legend.box.spacing = unit(-1, 'cm'),
        legend.margin = margin(0, 0, 0, 0, "cm"),
        panel.spacing.y = unit(1.3, "lines"),
        plot.margin = unit(c(0, -0.5, 0, -2), "lines") #top, right, bottom, left
        ) +
  facet_wrap(~issue, nrow = 6)


```


# Plot the number of resolutions in each issue over time 

```{r}
# Join resolutions to issues 
issues_resolutions <- issues %>%
  left_join(roll_calls, by = "rcid") %>%
  filter(year(date) > 1970) %>%
  # shorten issue names
  mutate(issue = recode(issue, "Nuclear weapons and nuclear material" = "Nuclear weapons and material"),
         issue = str_replace_all(issue, "and", "&"))
```


```{r}
# Number of resolutions per year split into issue 
hist <- issues_resolutions %>%
  ggplot() +
  aes(x = year(date)) +
  geom_area(stat = "count", aes(fill = issue)) +
  # add issue titles inside plot area
  geom_text(x = 1970, y = 45, 
            aes(label = issue), 
            data = issues_resolutions %>% distinct(issue), 
            hjust = 0, vjust = 1, 
            family = "Reenie Beanie", size = 7, fontface = "bold", colour = "#4f5157") +
  scale_fill_pomological() +
  theme_pomological(base_family = "Reenie Beanie", base_size = 20) +
  labs(x = "", y = "Number of UN resolutions per year",
       title = NULL) +
  facet_wrap(~issue, nrow = 6) +
  ylim(c(0, 45)) +
  theme(legend.position = "none", 
        panel.spacing.x = unit(2, "lines"),
        strip.text = element_blank(),
        plot.margin = unit(c(0.5, 0.5, 0, 0.5), "cm"), #top, right, bottom, left
        panel.border = element_blank()
        )

```



# Text analysis

Pick out the keywords from the UN resolutions within each issue by calculating tf-idf. 
```{r}
# Obtain tf idf for issues
issues_tf_idf <- issues %>%
  left_join(roll_calls, by = "rcid") %>%
  select(issue, descr) %>%
  unnest_tokens(word, descr) %>%
  # remove punctuation and amalgamate certain words
  mutate(word = str_remove_all(word, "[[:punct:]]"),
         word = case_when(
           str_detect(word, "test") ~ "testing",
           str_detect(word, "weapon") ~ "weapon",
           str_detect(word, "banning") ~ "ban",
          TRUE ~ word
         )) %>%
  count(word, issue) %>%
  bind_tf_idf(word, issue, n) %>%
  arrange(desc(tf_idf)) %>%
  # remove stopwords, numbers
  anti_join(stop_words, by = "word") %>%
  filter(!str_detect(word, "[0-9]"))


# issues_top_words <- issues %>%
#   left_join(roll_calls, by = "rcid") %>%
#   select(issue, descr) %>%
#   unnest_tokens(word, descr) %>%
#   mutate(word = str_remove_all(word, "[[:punct:]]"),
#          word = case_when(
#            str_detect(word, "palesti") ~ "palestine",
#            str_detect(word, "test") ~ "testing",
#            str_detect(word, "weapon") ~ "weapon",
#            str_detect(word, "banning") ~ "ban",
#           TRUE ~ word
#          )) %>%
#    anti_join(stop_words, by = "word") %>%
#   filter(!word %in% c("draft", "resolution")) %>%
#   count(word, issue) %>%
#   group_by(issue) %>%
#   slice_max(n, n = 10)

```


```{r}
# plot of tf_idf for resolutions under each issue 
tf <- issues_tf_idf %>%
  group_by(issue) %>%
  slice_max(tf_idf, n = 9) %>%
  mutate(word = reorder_within(word, tf_idf, issue)) %>%
  ungroup() %>%
  ggplot() +
  aes(x = tf_idf, y = word, fill = issue) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~issue, scales = "free_y", nrow = 6) +
  scale_fill_pomological() +
  scale_x_continuous(breaks = c(0, 0.005), labels = c(0, 0.005)) +
  theme_pomological(base_family = "Reenie Beanie", base_size = 20) +
  theme(strip.text = element_blank(),
        plot.margin = unit(c(0.5, 0, 0, 1), "cm"), #top, right, bottom, left
        panel.border = element_blank(),
        axis.ticks.x = element_line(colour = "#828585")
        ) +
  scale_y_reordered() +
  labs(y = NULL, 
       x = "tf-idf")
```



```{r}
# combine plots using patchwork
plot <- hist|tf|map

plot<- plot + plot_annotation(
  title = "UN General Assembly Resolutions Since 1970",
  subtitle = str_wrap("Using historical UN General Assembly Resolutions data, this visualisation shows the number of resolutions related to each issue over time, the keywords in those resolutions, and the proportion of resolutions each country voted \"yes\" for.", width = 90),
  theme = theme_pomological(base_family = "Reenie Beanie", base_size = 22)) +
  plot_layout(widths = c(1, 0.7, 1.5)) +
  theme(panel.border = element_blank(),
        panel.grid = element_blank(),
        strip.background = element_blank(),
        strip.placement = NULL)


# export as png
ggsave(here("UN_Votes_23-03-21/plot.png"), plot, height = 12, width = 11)
```
